---
title: "Project title"
author: "Team members names, tutorial section, and group number"
subtitle: "The subtitle of my project"
date: March 30, 2020
output: 
  beamer_presentation:
    theme: "Pittsburgh"
    colortheme: "orchid"
    fonttheme: "structurebold"
    slide_level: 2
---



```{r, echo=FALSE, message=FALSE, warning=FALSE}
# echo=FALSE will stop the code chunk from appearing in the knit document
# warning=FALSE and message=FALSE will stop R messages from appearing in the knit document
library(tidyverse)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load the TPS break in data
break_and_enters <- read_csv("break_and_enters.csv")
```


# A Section Heading on its own page

## A heading that starts on a new page

This document shows a few basics on making slides with R markdown.

To produce the slides, Knit to PDF (Beamer).

---

Three dashes starts a new page when it is not started by a new header. If you want to put a gap between parts of a slide `\vspace{0.3cm}` will do it. You can change the number inside the curly brackets 2 to get a smaller or larger gap.

\vspace{0.8cm}

### This is a heading that doesn't start a new page but makes a nice emphasis box

You can make text **bold** or in *italics*.

To make bullet points, start the points after a blank line:
 
- point one
- another point

## Markdown has nice formatting options for you

1. Check out the cheat sheet [https://github.com/rstudio/cheatsheets/raw/master/rmarkdown-2.0.pdf](https://github.com/rstudio/cheatsheets/raw/master/rmarkdown-2.0.pdf)
    i) Oh look! A sub-item in the list (note two 'tabs' before this line)
2. You can get help making tables here: [https://www.tablesgenerator.com/markdown_tables#](https://www.tablesgenerator.com/markdown_tables#)

| A column header | Another column header                |
|-----------------|--------------------------------------|
| First row       | First row, but now the second column |

### You can also use LaTeX commands
Roses are \textcolor{red}{red}, violets are \textcolor{blue}{blue}.
- column layouts
- font size for specific bits
- centering
- equations, inline or not inline e.g. equation of a line and and subsscprits like H_0

---

Include some R output

```{r}
ggplot(cars, aes(x=speed, y=dist)) + 
  geom_point()
```

---

Include the output without showing the code and R messages (which is what you want for your poster presentation).  This R code chunk also changes the size of the plot.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3}
ggplot(cars, aes(x=speed, y=dist)) + 
  geom_point()
```

This plot shows that there is a positive relationship between distance and speed.

## Read more

For more on creating a `beamer` presentation see [https://bookdown.org/yihui/rmarkdown/beamer-presentation.html](https://bookdown.org/yihui/rmarkdown/beamer-presentation.html)

You can change the style, colours and fonts in your presentation by picking from a library of available themes. Once you find ones you like, you change the settings in the YAML section at the top of this RMarkdown document.
[http://deic.uab.es/~iblanes/beamer_gallery/index.html](http://deic.uab.es/~iblanes/beamer_gallery/index.html) 


# Headings you should include in your project

## Introduction

Include here a few sentences to introduce the problem and provide context. You might want to briefly summarize the data in words (what is the data and what is it used for). You can present the questions you are investigating here. 

## Objectives (optional)

You can list the questions of interest in complete English sentences here to highlight them. 

## Data Summary (optional)

Here you can explain how you cleaned the data and created variables suitable for answering your questions. 
You can also include graphical displays that either motivated or address the questions.

## Statistical Methods

Describe here what you have done to the data without presenting any results (output). If you want to indicate variables by symbols or variable names, define them here. 

## Results

Present the main results here, in order of importance, related to the questions asked. You might use tables or graphs, or other ways to summarize your results.

## Conclusion

Give your main conclusions here. Follow the order of questions you presented. 

Here you can also mention any additional considerations, concerns, or issues you might have. For example, if the results were unexpected, you can discuss this and perhaps offer possible explanations.

## Acknowledgements (optional)

If you received any help from someone other than your team members you can acknowledge them. For example:   
*The authors would like to thank "TA name" for helpful suggestions and comments that improved the presentation of this poster.*


